### 2011-06-15 Spatial_adaptation/panmixia.tex
/* Comparison to panmixia */ see figures?

 \begin{figure}[hht]
  \includegraphics[width=0.8\textwidth]{min-s-versus-r.png}
 \caption{Plot of $s= 8 \left( \log(r)/r \right)^2$ against $r=\sqrt{A/\sigma^2}$.} 
 \end{figure}

To answer the second question, 
to expect parallel adaptation in the spatial case but not in the panmictic case,
we would clearly need $T_l \ll T_n$, so no new mutations are arising in the time to local fixation,
since this part of the process is shared by both.
Recall that this effectively puts an upper bound on $N$.
We'd also need
$T_s > T_n \gg T_p$,
or
\begin{equation}
  \sqrt{\frac{sA}{2\sigma^2}} > \frac{1}{4N\mu} \gg \log(A/\sigma^2) ,
\end{equation}
or
\begin{equation}
  % \sqrt{s/2} > \frac{1}{4 N \mu r} \gg 2 \frac{ \log(r) }{ r } .
  s > \frac{1}{8 N^2 \mu^2 r^2} \gg 8 \left(\frac{ \log(r) }{ r }\right)^2 .
\end{equation}
This puts an upper and lower bound on the mutational influx $4N\mu$:
taking the middle values in the figure, 
this will be something like $1/20 < 4N\mu < 800$.

@@

\includegraphics[width=1.0\textwidth]{f-versus-gamma}

@@

\includegraphics[width=0.8\textwidth]{gamma-contour-1e-8.png}

@@

\paragraph{In summary,}
the conclusions are:
\begin{enumerate}

@@

  \item Spatial structure can make parallel adaptation likely where it was unlikely under panmixia
    if the above does not happen and if
    $s > \frac{1}{8 N^2 \mu^2 r^2} \gg 8 \left(\frac{ \log(r) }{ r }\right)^2$;
    this latter restricts the range of mutational influxes, but not dramatically.

>>>>

 \begin{figure}[hht]
  \includegraphics[width=0.8\textwidth]{min-s-versus-r.pdf}
 \caption{Plot of $s= 8 \left( \log(r)/r \right)^2$ against $r=\sqrt{A/\sigma^2}$.} 
 \end{figure}

To answer the second question, 
to expect parallel adaptation in the spatial case but not in the panmictic case,
we would clearly need $T_l \ll T_n$, so no new mutations are arising in the time to local fixation,
since this part of the process is shared by both.
Recall that this effectively puts an upper bound on $N$.
We'd also need
$T_s > T_n \gg T_p$,
or
\begin{equation}
  \sqrt{\frac{sA}{2\sigma^2}} > \frac{1}{4N\mu} \gg \log(A/\sigma^2) ,
\end{equation}
or
\begin{equation}
  % \sqrt{s/2} > \frac{1}{4 N \mu r} \gg 2 \frac{ \log(r) }{ r } .
  s > \frac{1}{8 N^2 \mu^2 r^2} \gg 8 \left(\frac{ \log(r) }{ r }\right)^2 .
\end{equation}
This puts an upper and lower bound on the mutational influx $4N\mu$:
taking the middle values in the figure, 
spatial structure significantly increases the chance of parallel mutations if $1/20 < 4N\mu < 800$.

@@

\includegraphics[width=1.0\textwidth]{f-versus-gamma.pdf}

@@

\includegraphics[width=0.8\textwidth]{gamma-contour-1e-8.pdf}

@@

\paragraph{In summary,}
the conclusions are: (recall $r = \sqrt{A}/\sigma$)
\begin{enumerate}

@@

  \item Spatial structure can make parallel adaptation likely where it was unlikely under panmixia
    if the above does not happen and if
    $s > \frac{1}{8 (N \mu r)^2} \gg 8 \left(\frac{ \log(r) }{ r }\right)^2$;
    this latter restricts the range of mutational influxes, but not dramatically.
